学術論文

### 2022-11-01 articles.Rmd
update

@@

- [41] PSACR-001. (in press).
In COVID-19 health messaging, loss framing increases anxiety without concomitant benefits: Experimental evidence from 84 countries. Affective Science.

@@

>>>>

- [43] Buchanan, E. M., ... Kunisato, Y., ... Primbs, M. (in press).
The Psychological Science Accelerator's COVID-19 rapid-response dataset.
Scientific Data.

@@

@@

- [41] Dorison, C.A., Lerner, J.S., Heller, B.H... Kunisato, Y.,... Nicholas A. Coles (2022). In COVID-19 Health Messaging, Loss Framing Increases Anxiety with Little-to-No Concomitant Benefits: Experimental Evidence from 84 Countries. Affective Science. [link](https://doi.org/10.1007/s42761-022-00128-3)
